plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-10-12 manuscript.Rmd
2nd round revisions done, I think?

# This document can be compiled with the 'Knit Word' button in Rstudio, or:
# library(rmarkdown)
# render("manuscript.Rmd", "word_document", "manuscript.docx")
```

@@

\
In the practical application of the FvCB model, it is often assumed that C~c~ is equal to the intercellular [CO~2~] concentration (C~i~), which is useful because C~i~ can be estimated from leaf gas exchange data [@sharkey1982], and it avoids the need to estimate the conductance from intercellular airspaces to the chloroplast (mesophyll conductance, g~m~). In the remainder of this article I will use C~c~ as the driver of photosynthesis, but point out that this can be replaced by C~i~ if the user does not have an estimate of g~m~. When g~m~ is known, C~c~ is calculated from C~i~ with Eq. 2.

@@

```{r eval=TRUE, echo=FALSE, message=FALSE}
acidata1$PPFD <- 1800
myfit <- suppressWarnings(fitaci(acidata1))
fitc <- myfit$pars
```

\
**Figure 2**. Standard output from the `fitaci` function. A~n~ is the net photosynthetic rate, C~i~ the intercellular CO~2~ concentration. Symbols are measurements, the black line the fitted FvCB model of photosynthesis. Colored lines indicate the two photosynthesis rates in the FvCB model. In the default mode, the `fitaci` function estimates V~cmax~, J~max~ and R~d~ from the fitted curve. Optionally, R~d~ is provided as an input, for example when it was measured separately. In this example, V~cmax~ was estimated as `r round(fitc["Vcmax","Estimate"],1)` (SE `r round(fitc["Vcmax","Std. Error"],2)`), J~max~ was `r round(fitc["Jmax","Estimate"],1)` (SE `r round(fitc["Jmax","Std. Error"],2)`) and R~d~ was `r round(fitc["Rd","Estimate"],1)` (SE `r round(fitc["Rd","Std. Error"],2)`) (all in units of $\mu$mol m^-2^ s^-1^).

@@

\
To demonstrate the use of the coupled gas exchange model, I visualize the temperature response of A~n~ when both T~leaf~ and D are varying. In field conditions, D is always strongly positively related to T~leaf~. The consequence is that when studying D or T~leaf~ responses in the field, both drivers have to be accounted for simultaneously [@lin2012; @duursma2014]. Figure 3a shows simulated A-C~i~ curves and the solutions of the coupled leaf gas exchange models at a range of T~leaf~ and corresponding D (calculated following [@duursma2014]). Figure 3b shows the output from `Photosyn`, which can be created with the following example. Note that in this example the default values of many parameters (e.g. J~max~, g~1~) are used in the call to `Photosyn`, but all of these can be set by the user.

@@

>>>>

# This document can be compiled with the 'Knit Word' button in Rstudio, or:
# library(rmarkdown)
# render("manuscript.Rmd", "word_document", "manuscript.docx")
# which assumes you have Pandoc installed (unless you run this from Rstudio),
# and that you have an internet connection.

@@

\
In the practical application of the FvCB model, when leaf gas exchange is measured with a portable gas exchange instrument, estimates of C~c~ are difficult to obtain because they require an estimate of the mesophyll conductance. In this case, it is customary to us the intercellular [CO~2~] concentration (C~i~) as the driver of photosynthesis. This approach is useful because C~i~ can be estimated from concurrent measurements of CO~2~ and H~2~O flux [@sharkey1982]. In the remainder of this article I will use C~c~ as the driver of photosynthesis, but point out that this can be replaced by C~i~ if the user does not have an estimate of g~m~. When this is is known, C~c~ is calculated from C~i~ with Eq. 2.

@@

```{r eval=TRUE, echo=FALSE, message=FALSE}
# acidata1 is an example dataset in plantecophys (see ?acidata1)
acidata1$PPFD <- 1800
exfit1 <- suppressWarnings(fitaci(acidata1))
fitc <- exfit1$pars
```

\
**Figure 2**. Standard output from the `fitaci` function. A~n~ is the net photosynthetic rate, C~i~ the intercellular CO~2~ concentration. Symbols are measurements, the black line the fitted FvCB model of photosynthesis. Colored lines indicate the two photosynthesis rates in the FvCB model. In the default mode, the `fitaci` function estimates V~cmax~, J~max~ and R~d~ from the fitted curve. Optionally, R~d~ is provided as an input, for example when it was measured separately. In this example, V~cmax~ was estimated as `r round(fitc["Vcmax","Estimate"],1)` (SE `r round(fitc["Vcmax","Std. Error"],2)`), J~max~ was `r round(fitc["Jmax","Estimate"],1)` (SE `r round(fitc["Jmax","Std. Error"],2)`) and R~d~ was `r round(fitc["Rd","Estimate"],1)` (SE `r round(fitc["Rd","Std. Error"],2)`). Assumed parameters were K~m~ = `r round(exfit1$Km,0)` and $\Gamma}^{∗}$ = `r round(exfit1$GammaStar,1)` (all in units of $\mu$mol m^-2^ s^-1^). The R^2^ of a regression of measured vs. fitted was 0.99.

@@

\
To demonstrate the use of the coupled gas exchange model, I visualize the temperature response of A~n~ when both T~leaf~ and D are varying. In field conditions, D is always strongly positively related to T~leaf~. The consequence is that when studying D or T~leaf~ responses in the field, both drivers have to be accounted for simultaneously [@lin2012; @duursma2014]. Figure 3a shows simulated A-C~i~ curves and the solutions of the coupled leaf gas exchange models at a range of T~leaf~ and corresponding D (calculated following [@duursma2014]). Both V~cmax~ and J~max~ have a peaked response to T~leaf~, so that at a given C~i~, A~n~ first increases with T~leaf and then decreases (lines, Fig. 3a). As a result of increasing D, the modelled C~i~ decreases (symbols, Fig. 3a). The net result is a peaked response of A~n~ as a function of D (Fig. 3b).

@@

The simplified code to produce Figure 3b, using the `Photosyn` function, is given below. Note that in this example the default values of many parameters (e.g. J~max~, g~1~) are used in the call to `Photosyn`, but all of these can be set by the user.
